Wired for Success: Sweden's Electrical Innovators in the Age of Industrial Transformation

### 2023-05-15 index.qmd
add names

---
title: "Wired for Success: Sweden's Electrical Innovators in the Age of Industrial Transformation"
title-slide-attributes:
  data-background-image: "assets/preview.png"
  data-background-size: "30%"
  data-background-opacity: "0.6"
format: 
  revealjs:
    code-overflow: wrap
    width: 1600
    height: 900
    fig-align: center
    default-image-extension: svg
    footer: "[{{< fa house >}}](https://j-jayes.github.io/Data-Visualization-in-R-Lund/)"
    slide-number: c
    code-block-bg: true
    code-block-border-left: "#31BAE9"
image: "preview_img/03-coordinate-systems-and-axes.jfif"
favicon: html/favicon.ico
---

@@

```{css}
code.sourceCode {
  font-size: 1.3em;
  /* or try font-size: xx-large; */
}
```

@@

TODO: fix names

```{python, eval=FALSE, echo=TRUE}
{
    "original": "Axell, Folke Adolf, civilingenjör, Norrköping, f. 4/12/08 i Ljusnarsberg, Örebro 1. G. 36 m. Marianne Hammarberg. Barn: Anita f. 37, Peter 42. — Avg:ex. fr. tekn. gymn. i Örebro 28, civ:ing:ex. v. KTH 34. Ing:assist. v. telegr :v. i Nässjö 35, linjeing. v. te-legr :v. i Norrköp. sed. 46. Led. av Sv. tekn :fören. sed. 35.",
    "translated": "Axell, Folke Adolf, engineer, from Norrköping, born on December 4th, 1908 in Ljusnarsberg, Örebro 1. Married in 1936 to Marianne Hammarberg. Children: Anita born in 1937, Peter born in 1942. He graduated from the Technical Gymnasium in Örebro in 1928, received his engineering degree from KTH in 1934. Worked as an engineering assistant at the telegraph station in Nässjö in 1935, and as a line engineer at the telegraph station in Norrköping since 1946. Member of the Swedish Technical Association since 1935.",
    "structured": {
        "@context": "https://schema.org",
        "@type": "Person",
        "name": "Folke Adolf Axell",
        "birthDate": "1908-12-04",
        "birthPlace": {
            "name": "Ljusnarsberg, Örebro",
            "latitude": 59.916667,
            "longitude": 15.0
        },
        "jobTitle": "Engineer",
        "memberOf": {
            "@type": "Organization",
            "name": "Swedish Technical Association"
        },
        "children": [
            {
                "@type": "Person",
                "name": "Anita",
                "birthDate": "1937"
            },
            {
                "@type": "Person",
                "name": "Peter",
                "birthDate": "1942"
            }
        ],
        "spouse": {
            "@type": "Person",
            "name": "Marianne Hammarberg",
            "marriageDate": "1936"
        },
        "education": [
            {
                "@type": "EducationalOccupationalCredential",
                "credentialCategory": "Vocational",
                "issuer": {
                    "@type": "Organization",
                    "name": "Technical Gymnasium in Örebro"
                },
                "endDate": "1928"
            },
            {
                "@type": "EducationalOccupationalCredential",
                "credentialCategory": "Degree",
                "issuer": {
                    "@type": "Organization",
                    "name": "KTH"
                },
                "endDate": "1934"
            }
        ],
        "worksFor": {
            "@type": "Organization",
            "name": "Telegraph station in Norrköping",
            "startDate": "1946"
        },
        "hasOccupation": [
            {
                "@type": "Occupation",
                "name": "Engineering assistant",
                "employer": {
                    "@type": "Organization",
                    "name": "Telegraph station in Nässjö"
                },
                "startDate": "1935",
                "endDate": "1935"
            },
            {
                "@type": "Occupation",
                "name": "Line engineer",
                "employer": {
                    "@type": "Organization",
                    "name": "Telegraph station in Norrköping"
                },
                "startDate": "1946"
            }
        ]
    }
}
```

@@

>>>>

---
title: "Wired for Success: Sweden's Electrical Innovators in the Age of Industrial Transformation"
subtitle: "CBS Department of Strategy and Innovation Graduate Seminar"
author: "Jonathan Jayes  - Lund University"
title-slide-attributes:
  data-background-image: "assets/preview.png"
  data-background-size: "30%"
  data-background-opacity: "0.6"
format: 
  revealjs:
    code-overflow: wrap
    width: 1600
    height: 900
    fig-align: center
    default-image-extension: svg
    footer: "[{{< fa house >}}](https://j-jayes.github.io/Data-Visualization-in-R-Lund/)"
    slide-number: c
    code-block-bg: true
    code-block-border-left: "#31BAE9"
image: "preview_img/03-coordinate-systems-and-axes.jfif"
favicon: html/favicon.ico
---

@@

@@

```{python, eval=FALSE, echo=TRUE}
#| code-line-numbers: "6-14"

{
    "original": "Lund, Karl Gustaf, överingenjör, Varberg, f. 22/7/93 i Hille, Gävleb. 1., av brukstj :m. Ferdinand L. o. Maria Andersson. G. 36 m. Sigrid Johansson. Barn: Ingvar f. 38, Lennart 42. — Ex. v. bergssk. i Filipstad 17, spec:-stud. v. KTH (B) 20-22, stud. v. me-tallogr. inst. o. Sthlms högsk. 21-22. Kemist v. Strömsnäs Järnverks A-B, Degerfors, 18-20, metallurg o. kemist v. Westinghouse Electric & Manuf. Co., East Pittsburgh, Pa, USA, 23-26 o. 28-29, chefsmetallurg v. Laclede Steel^Co., Ahon, 111., USA, 27, hytt-o. stålv.ing. v. A-B Iggesunds Bruk 29-31, platschef v. Gunnebo Bruks Nya A-B, Varbergsverket, sed. 31. Led. av drätselkamm., v. ordf. v. ekonomi-avd., suppl. i styr. f. elverket, huv:-man i Varbergs Sparbank, arb :giv. repr. i länsarb:ndns kretsråd, led. av styr. f. Varbergs luftsk ifören., sekr. i Varbergs högerfören., ordfs i järnv. sjukkassa o. Plant :sällsk. Småfågl. Vänner. Res. t. Tyskl. 21, 2^ 23, 30 o. 36, Danm., Tjeckoslov. 21, 22, 23, Österr. 21, USA 23-29. Skr.: Some fundamental factors for obtaining sharp thermal curves (Träns. Am. Soc. for Steel Treating, tills. m. C. Benedicks o. W. H. Dearden 25), Nutida fabrikation av sågblad, sågklingor o. maskinknivar (Trävaruind. 31). Hob-bies: jakt o. fiske.",
    "translated": "Lund, Karl Gustaf, chief engineer, Varberg, born on July 22, 1893, in Hille, Gävle County, Sweden, son of factory worker Ferdinand L. and Maria Andersson. Married in 1936 to Sigrid Johansson. Children: Ingvar (born 1938), Lennart (born 1942). — Graduated from Bergsskolan in Filipstad in 1917, specialized studies at the Royal Institute of Technology (KTH) from 1920 to 1922, studied at the Institute of Metallurgy and Stockholm University in 1921-1922. Chemist at Strömsnäs Järnverks A-B in Degerfors from 1918 to 1920.",
    "structured": {
        "@context": "https://schema.org",
        "@type": "Person",
        "name": "Karl Gustaf Lund",
        "birthDate": "1893-07-22",
        "birthPlace": {
            "name": "Hille, Gävle County, Sweden",
            "latitude": 59.916667,
            "longitude": 15.0
        },
        "jobTitle": "Chief Engineer",
        "memberOf": {
            "@type": "Organization",
            "name": "Swedish Technical Association"
        },
        "children": [
            {
                "@type": "Person",
                "name": "Anita",
                "birthDate": "1937"
            },
            {
                "@type": "Person",
                "name": "Peter",
                "birthDate": "1942"
            }
        ],
        "spouse": {
            "@type": "Person",
            "name": "Marianne Hammarberg",
            "marriageDate": "1936"
        },
        "education": [
            {
                "@type": "EducationalOccupationalCredential",
                "credentialCategory": "Vocational",
                "issuer": {
                    "@type": "Organization",
                    "name": "Technical Gymnasium in Örebro"
                },
                "endDate": "1928"
            },
            {
                "@type": "EducationalOccupationalCredential",
                "credentialCategory": "Degree",
                "issuer": {
                    "@type": "Organization",
                    "name": "KTH"
                },
                "endDate": "1934"
            }
        ],
        "worksFor": {
            "@type": "Organization",
            "name": "Telegraph station in Norrköping",
            "startDate": "1946"
        },
        "hasOccupation": [
            {
                "@type": "Occupation",
                "name": "Engineering assistant",
                "employer": {
                    "@type": "Organization",
                    "name": "Telegraph station in Nässjö"
                },
                "startDate": "1935",
                "endDate": "1935"
            },
            {
                "@type": "Occupation",
                "name": "Line engineer",
                "employer": {
                    "@type": "Organization",
                    "name": "Telegraph station in Norrköping"
                },
                "startDate": "1946"
            }
        ]
    }
}

@@

## Questions I need to answer

1. What is an innovator in this context?

2.
